Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-30 dit-paper_ieee.tex
algo gaussssssss

\algsetup{
  indent=2em,
  linenosize=\small,
  linenodelimiter=\
}

@@

	\subsection{Solving the modular system}
		Finding the FPDIT of a system is similar to finding at least one synchronous
		instant (an instant at which all tasks release a job simultaneously) out of a
		collection of systems with different offsets. The existence conditions can
		directly be used to calculate the value of the FPDIT (if there is one),
		because for a given set of $a_i$ values they are very similar to an instance
		of the Chinese Remainder Problem (CRP), which is easily solved using Gauss's
		CRP solving method for non-coprime $T_i$ \cite{gauss1965disquisitiones}.

		However this is very inefficient as there are exponentially many different
		combinations of $a_i$ values in the number of tasks. A better method for finding the FPDIT consists in splitting Gauss's
		algorithm into two separate parts. Its global structure is simply a sum of
		factors, each term being dependent on which $a_i$ value is chosen. A major speedup can
		be achieved by first computing all possible terms for each task then creating all
		possible DIT values by summing the terms in all possible ways. The number of results is still
		exponential in the number of tasks, but the only operation that is repeated
		exponentially many times is now a sum.

>>>>

\algsetup{
  indent=1em,
  linenosize=\small,
  linenodelimiter=\
}

@@

	\subsection{Solving the modular system}
		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
		the FPDIT (if there is one), because for a given set of $a_i$ values they are
		very similar to an instance of the Chinese Remainder Problem (CRP), which is
		easily solved using Gauss's CRP solving method for non-coprime moduli
		\cite{gauss1965disquisitiones}.

		However this is very inefficient as there are exponentially many different
		combinations of $a_i$ values in the number of tasks, and resolving
		exponentially many CRP is prohibitively slow. A better method for finding the
		FPDIT consists in splitting Gauss's algorithm into two separate parts, as
		shown in Algorithm~\ref{alg:multiACRP}.

		\begin{algorithm}
			\caption{Modified Gauss Algorithm}
			\label{alg:multiACRP}
			\begin{algorithmic}[1]
				\REQUIRE $A$ is a list of the sets of possible $a_i$ per task
				\REQUIRE $H$ is the hyperperiod of the system

				\STATE $sumchunks \leftarrow \text{empty list}$
				\FORALL{$\tau_j \in \tau$}
					\STATE $taskTerms \leftarrow \text{empty list}$ 
					\STATE $Mj \leftarrow \frac{H}{T_j}$
					\STATE $invMj \leftarrow Mj^{-1} (mod \; T_j)$
					\FORALL{$a_i \in A(\tau_j)$}
						\STATE $\text{append} \; (a_i \cdot Mj \cdot invMj) \; \text{to} \; taskTerms$
					\ENDFOR
					\STATE $\text{append} \; taskTerms \; \text{to} \; sumchunks$
				\ENDFOR

				\STATE $results \leftarrow \text{empty list}$
				\STATE append $0$ to $results$
				\FORALL{$\tau_j \in \tau$}
					\STATE $newresults \leftarrow \text{empty list}$
					\FORALL{$a_i \in A(\tau_j)$}
						\FORALL{$r \in results$}
							\STATE $\text{append} \; (r + sumchunks(\tau_j,i)) \; \text{to} \; newresults$
						\ENDFOR
					\ENDFOR
					\STATE $results \leftarrow newresults$
				\ENDFOR
				\RETURN $r \; (mod \; H)$ for all $r \in results$
			\end{algorithmic}
		\end{algorithm}

		The global structure of the original algorithm is simply a sum of factors, each term being dependent on which $a_i$ value is chosen. A major
		speedup is achieved by first computing all possible terms for each task
		then creating all possible DIT values by summing the terms in all possible
		ways. The number of results is still exponential in the number of tasks, but
		the only operation that is repeated exponentially many times is now a sum.
		This allows us to profit from the high chance of having DITs when the CDF
		factor is close to one, but with only a slight increase in computation time as the sizes of the $[D_i, T_i]$ intervals grow.
